---
title: "Test"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
library(ggplot2)
```

## Binomial Distribution

The package `"binomial"` is a minimal implementation for simulating binomial distribution, given the number of trials and the probability. It provides a series of related functions to help better illustrate the binomial distribution.

## Creating a bin_variable

You can create a `"binomial variable"` object with the function `bin_variable()`. You can change the arguments `trials` and `prob` to get any binomial variable you want:

```{r}
#create a binomial variable with number of trials and the probability
my_var <- bin_variable(trials=10,prob=0.5)
my_var
```
You can also know the overall probability given the number of success, the number of trials and the probability with the function `bin_probability` and the arguments `success`, `trials` and `prob`
```{r}
prob <- bin_probability(trials=10,success=5,prob=0.5)
prob
```


You can know the number of combinations given the number of trails and success and you can change the arguments `n` and `k` to the value you want:

```{r}
num_comb <- bin_choose(n=10,k=3)
num_comb
```
## Summary
The `summary()` function gives you a nice table of related measures e.g. mean,variance,mode,skewness, kurtosis:

```{r}
summary(my_var)
```
## Related Measurements

The `bin_mean` function gives you the mean of the binomial distribution given arguments `trials` and `prob`:
```{r}
bin_mean(trials=10,prob=0.5)
```
The `bin_variance` function gives you the variance of the binomial distribution given arguments `trials` and `prob`:
```{r}
bin_variance(trials=10,prob=0.5)
```

The `bin_mode` function gives you the mode of the binomial distribution given arguments `trials` and `prob`:
```{r}
bin_mode(trials=10,prob=0.5)
```
The `bin_skewness` function gives you the skewness of the binomial distribution given arguments `trials` and `prob`:
```{r}
bin_skewness(trials=10,prob=0.5)
```

The `bin_kurtosis` function gives you the kurtosis of the binomial distribution given arguments `trials` and `prob`:
```{r}
bin_kurtosis(trials=10,prob=0.5)
```
## Create a binomial distribution

You can create a binomial distribution with the function `bin_distribution` given the arguments of `trials` and `prob` and use function `plot` to draw a plot for binomial distribution:

```{r}
my_bin_dis <- bin_distribution(trials=10,prob=0.5)
my_bin_dis
plot(my_bin_dis)
```

You can also create a cumulative binomial distribution with the function `bin_cumulative` and arguments are `trials` and `prob`. Then use function `plot` to draw a plot for that:
```{r}
my_bin_cum <- bin_cumulative(trials=10,prob=0.5)
my_bin_cum
plot(my_bin_cum)
```

