---
title: "README"
author: "yilin-wu"
date: "May 3, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
`"binomial"` is a minimal R package that provides some related functions and measurements for binomial distribution.

`"bin_variable()"` creates a binomial object with arguments `trials` and `prob`
`"bin_probability()"` calculates the probability given `success` , `trials` and `prob`
`"bin_choose()"` calculates the number of combination given `n` and `k`
`"summary()"` gives the summary of that binomial object
`"bin_mean()"` gives the mean given `trials` and `prob`
`"bin_variance()"` gives the variance given `trials` and `prob`
`"bin_mode()"` gives the mode given `trials` and `prob`
`"bin_skewness()"` gives the skewness given `trials` and `prob`
`"bin_kurtosis()"` gives the kurtosis given `trials` and `prob`
`"bin_distribution()"` returns the binomial distribution
`"bin_cumulative()"` returns the cumulative probability for binomial distribtuion
`"plot()"` returns a barplot for bin_distribution and scatterplot with line for bin_cumulative


## Motivation
This package has been developed to illustrate some of the concepts behind the creation of an R package.


## Installation
Install the development version from GitHub via the package "devtools":
```{r}
# development version from GitHub:
#install.packages("devtools") 

# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-yilin-wu98/tree/master/workout03/binomial")

# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-yilin-wu98/tree/master/workout03/binomial", build_vignettes = TRUE)

```


## Usage
```{r}
library(binomial)
library(ggplot2)
#create a binomial variable with number of trials and the probability
my_var <- bin_variable(trials=10,prob=0.5)
my_var
prob <- bin_probability(trials=10,success=5,prob=0.5)
prob
num_comb <- bin_choose(n=10,k=3)
num_comb
summary(my_var)
bin_mean(trials=10,prob=0.5)
bin_variance(trials=10,prob=0.5)
bin_mode(trials=10,prob=0.5)
bin_skewness(trials=10,prob=0.5)
bin_kurtosis(trials=10,prob=0.5)
my_bin_dis <- bin_distribution(trials=10,prob=0.5)
my_bin_dis
plot(my_bin_dis)
my_bin_cum <- bin_cumulative(trials=10,prob=0.5)
my_bin_cum
plot(my_bin_cum)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
